---
title: "Class4_mynotes"
output: word_document
---

renaming levels of a factor:
```{r}
mysleep <- sleep
summary(mysleep)
head(mysleep)
levels(mysleep$group)
levels(mysleep$group)<- c("a", "b")
summary(mysleep)

paste("s", "1", sep = "") # pasting strings together
paste("s", mysleep$ID, sep = "")  #sep specifies the separator. it's null (no space) here.
factor(paste("s", mysleep$ID, sep = "")) #coercing into factor.
mysleep$ID <- factor(paste("s", mysleep$ID, sep = ""))
summary(mysleep)



```

## 
droplevles() drops (the whole row of) levels (of any factor column in the data file) that have a value of zero.

identical() checks if two arguments (2 columns for example) are identical or not.

length(sleep): treating data frame like a list. This will return the objects inside the list and not theri contents (values of the columns).

assigning NULL to a column in a data frame (or to anything else) will get rid of it (that column will be deleted).


help ("colnames")
help ("colnames<-")

```{r}


```

