---
title: "Final Project"
author: "Minoo Ahmadi"
date: "January 19, 2017"
output: html_document
---
Power analysis
A bunch of regressions and plotting.


```{r "setup", include=FALSE}
require("knitr")
opts_knit$set(root.dir = "~/gits/project/")
```
## Power analysis for a regression analysis
Regress Dominance congruence effect on social anxiety scores (SPS, SIAS, BFNE) and domoinance level (IPIP_Domineering. 

``` {r}

df.num <- 3 # number of continuous variables (predictors)
df.denom <- # create a vecor? this is what we're looking for
eff.size <- .15 # medium effect size
p.val <- .05
pow <- .8







```

First, simulating data for a logistic regression:

```{r}
set.seed(1)

repetitions = 1000
N = 10000
n = N/8
var1  = c(   .03,    .03,    .03,    .03,    .06,    .06,    .09,   .09)
var2  = c(     0,      0,      0,      1,      0,      1,      0,     1)
rates = c(0.0025, 0.0025, 0.0025, 0.00395, 0.003, 0.0042, 0.0035, 0.002)

var1    = rep(var1, times=n)
var2    = rep(var2, times=n)
var12   = var1**2
var1x2  = var1 *var2
var12x2 = var12*var2

significant = matrix(nrow=repetitions, ncol=7)

for(i in 1:repetitions){
  responses<- rbinom(n=N, size=1, prob=rates)
  model<- glm(responses~var1+var2+var12+var1x2+var12x2, family=binomial(link="logit"))
  significant[i,1:5]<- (summary(model)$coefficients[2:6,4]<.05)
  significant[i,6]<- sum(significant[i,1:5])
  modelDev<- model$null.deviance-model$deviance
  significant[i,7]<- (1-pchisq(modelDev, 5))<.05
}



```

The example for t.test:
```{r}
n.sim <- 10000
sample.n <- 100
mean.difference <- .3
sd.x <- 1
sd.y <- 1

results <- data.frame(iteration = 1:n.sim, p.ttest = NA, p.wilcox = NA)

for(counter in 1:n.sim) {
  this.x <- rnorm(sample.n, mean = 0, sd = sd.x)
  this.y <- rnorm(sample.n, mean = mean.difference, sd = sd.y)
  this.ttest <- t.test(this.x, this.y)
  this.wilcox <- wilcox.test(this.x, this.y)
  results[counter, "p.ttest"] <- this.ttest$p.value
  results[counter, "p.wilcox"] <- this.wilcox$p.value
  if(counter %% 500 == 0) {
    print(paste("finished simulation #", counter))
  }
}
head(results)
results$ttestsig <- ifelse(results$p.ttest < .05, TRUE, FALSE)
results$wilcoxsig <- ifelse(results$p.wilcox < .05, TRUE, FALSE)
head(results)
sum(results$ttestsig)/nrow(results)
sum(results$wilcoxsig)/nrow(results)


```



The example for correlation:

``` {r}
# set up the parameters of the simulation
n.sim <- 10000
sample.ns <- 100:200
correlation <- .2

power.analysis.results <- data.frame(sample.size = sample.ns, power = NA)

#for(this.sample in sample.ns) {
  cortable <- matrix(c(1, correlation, correlation, 1), ncol = 2)
  # "pre-allocate" the results table
  results <- data.frame(iteration = 1:n.sim, p = NA)
  
  for(counter in 1:n.sim) {
    this.data <- as.data.frame(mvrnorm(this.sample, mu = c(0, 0), Sigma = cortable))
    this.cortest <- cor.test(this.data$V1, this.data$V2)
    results[counter, "p"] <- this.cortest$p.value
    if(counter %% 500 == 0) {
      print(paste("finished simulation #", counter))
    }
  }
  #head(results)
  results$sig <- ifelse(results$p < .05, TRUE, FALSE)
  #head(results)
  power.analysis.results[power.analysis.results$sample.size == this.sample, "power"] <-   sum(results$sig)/nrow(results)

}

head(power.analysis.results)

power.threshold <- .9

min.sample <- min(power.analysis.results$sample.size[power.analysis.results$power >= power.threshold])
ggplot(power.analysis.results, aes(sample.size, power)) + geom_line() + 
  geom_smooth(se = FALSE, method = "loess") + 
  geom_hline(yintercept = max(power.analysis.results$power), color = "red") +
  annotate("text", x = min(power.analysis.results$sample.size) + (max(power.analysis.results$sample.size) - min(power.analysis.results$sample.size))/2, y = 1.02, label = paste("max power in these simulations:", max(power.analysis.results$power))) +
  geom_hline(yintercept = power.threshold, color = "red", linetype = 2) + 
  annotate("text", x = min(power.analysis.results$sample.size) + (max(power.analysis.results$sample.size) - min(power.analysis.results$sample.size))/2, y = power.threshold + .02, label = paste("sample needed for", power.threshold, " power:", min.sample))
    

```













## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Dominance Congruency effect (200, 400, 800): gather. 3 levels.

power = sig tests/totall tests
effect size for multiple regression: f^2 = R^2/1-R^2 (sort of an odds ratio)

Regress Dominance congruence effect on social anxiety scores (SPS, SIAS, BFNE), dominance level (IPIP_Domineering). f^2 =  .207/1-.207 = .261

install.packages("pwr")
library(pwr)
pwr.f2.test (1,25, .261, .05, power = NULL)

     Multiple regression power calculation 

              u = 1
              v = 25
             f2 = 0.261
      sig.level = 0.05
          power = 0.7229382


Means:
BFN: 22
SPS: 31
SIAS: 42




pwr.f2.test (1,25, f2= NULL, .05, .8)

     Multiple regression power calculation 

              u = 1
              v = 25
             f2 = 0.3147446
      sig.level = 0.05
          power = 0.8
          

Function: pwr.f2.test 
Arguments: 
u: Numerator degrees of freedom (the number of continuous predictors plus the number of dummy variables minus one) 
v: Denominator (error) degrees of freedom  
f2: Effect Size (Cohen suggests f2 values of 0.02, 0.15, and 0.35 represent small, medium, and large effect sizes). 
sig.level: Significance level power: Power of test

pwr.f2.test(u = 3, v = NULL, f2 = .15, sig.level = 0.05, power = 0.8)

     Multiple regression power calculation 

              u = 3
              v = 72.70585
             f2 = 0.15
      sig.level = 0.05
          power = 0.8
          
==> 73+3+1=77 is the require sample size for getting a power of .8 with 3 continuous variables.

