---
title: "Day 7 Homework"
output: html_document
---

Find three relationships in your data.  For each relationship, do the following:

1. Verbally articulate the relationship you want to examine.

BIS and BFNE: Is there arelationship between behavioral inhibition and fear of negative evaluation? Do males and females differ regarding this relationship?

BFNE and SPS_SIAS_Total: Is there arelationship between fear of negative evaluation and the other measure of social anxiety (positive correlation)? Do males and females differ regarding this relationship?


IPIP_Domineering and BAS_Reward_Responsiveness: Are dominance levle and reward responsiveness related (negative correlation)? Do males and females differ regarding this?

2. Verbally identify what variables you want to map to each graphical dimension.

x: BIS
y: BFNE

x: BFNE 
y: SPS_SIAS_Total

x: IPIP_Domineering 
y: BAS_Reward_Responsiveness

3. Reshape your data as needed.

no reshaping is needed, because my only factor variable is sex which has string values of male and female and not numerical values. (I could use 0 and 1 values, but that doesn't seem interesting)

4. Use ggplot2 to create your graphs.

``` {r}
library (haven)
getwd() 
setwd("C:/Users/ahmadi/Documents/Courses/PSYC798W/PSYC798W_R_Winter_2017/Data")
my.data<- read_sav("Data_FYP.sav")

ggplot(my.data, aes(x = BIS, y = BFNE)) + geom_bar(stat = "identity", aes(fill = Sex))

ggplot(my.data, aes(BFNE, SPS_SIAS_Total)) + geom_point(aes(color = Sex), size = 4) + geom_smooth(method = "lm", aes(color = Sex))

ggplot(my.data, aes(IPIP_Domineering, BAS_Reward_Responsiveness)) + geom_point(aes(color = Sex), size = 6) + geom_smooth(method = "loess", aes(color = Sex))

```

5. Fiddle with colors, axis labels, themes, etc. until the plot looks "publication ready" to you.  Try to change at least one thing per plot.

``` {r}
ggplot(my.data, aes(x = BIS, y = BFNE)) + geom_bar(stat = "identity", aes(fill = Sex) , position = "dodge")+ theme_classic()

ggplot(my.data, aes(BFNE, SPS_SIAS_Total)) + geom_point(aes(color = Sex), size = 4) + geom_smooth(method = "lm", aes(color = Sex))+ set1.colors

ggplot(my.data, aes(IPIP_Domineering, BAS_Reward_Responsiveness)) + geom_point(aes(color = Sex), size = 6) + geom_smooth(method = "loess", aes(color = Sex))+ scale_color_manual(values = c("magenta", "blue"))+ scale_x_continuous(name = "Dominance Level") + scale_y_continuous(name = "Reward Responsiveness")+ theme_minimal() + theme(legend.position = "top")

```

6. Save all plots to a format that you could use in a paper.  HINT: PNG works well for pasting into Word documents.

``` {r}
savePlot(filename = "CorrelationPlots", type = "png") # this returned an error: Error in savePlot(filename = "CorrelationPlots", type = "png") : can only copy from 'windows' devices

# so I used this one:
dev.copy(png, 'CorrelationPlots.png')
dev.off

```
